Local PCA Shows How the Effect of Population Structure Differs Along the Genome

### 2017-07-30 writeup/local_pca_paper.tex
moved over to new argrecorder set-up

\begin{table}[ht]
\centering
    \begin{tabular}{p{0.8in}rrrr}
  \hline
    species 
    & \parbox[t]{.8in}{\# SNPs per \\ window} 
    & \parbox[t]{1in}{mean window\\ length (bp)}
    & \parbox[t]{1.2in}{mean \# windows \\ per chromosome} 
    & \parbox[t]{1.4in}{mean \% variance ex-\\plained by top 2 PCs} \\ 
  \hline
  \textit{Drosophila melanogaster} & 1,000 & 9,019 & 2,674 & 0.53 \\ 
  Human & 100 & 636,494 & 203 & 0.55 \\ 
  \textit{Medicago truncatula} & 10,000 & 102,580 & 467 & 0.50 \\ 
   \hline
\end{tabular}
\caption{
    Descriptive statistics for each dataset used.
    % with the chosen window sizes.
    % See text for how window sizes were chosen;
    Columns 2--4 give statistics describing the window sizes used for most analyses for each dataset
    (windows had a fixed number of SNPs).
    The final column gives the percent variance explained by the top two principal components,
    averaged across independent PCA of each window.
    \label{tab:data_stats}
}
\end{table}

@@

>>>>

\begin{table}[ht]
\centering
    \begin{tabular}{p{0.8in}rrrr}
  \hline
    species 
    & \parbox[t]{.8in}{\# SNPs per \\ window} 
    & \parbox[t]{1in}{mean window\\ length (bp)}
    & \parbox[t]{1.2in}{mean \# windows \\ per chromosome} 
    & \parbox[t]{1.4in}{mean \% variance ex-\\plained by top 2 PCs} \\ 
  \hline
  \textit{Drosophila melanogaster} & 1,000 & 9,019 & 2,674 & 0.53 \\ 
  Human & 100 & 636,494 & 203 & 0.55 \\ 
  \textit{Medicago truncatula} & 10,000 & 102,580 & 467 & 0.50 \\ 
   \hline
\end{tabular}
\caption{
    Descriptive statistics for each dataset used.
    \revpoint{2}{18}
    % % with the chosen window sizes.
    % % See text for how window sizes were chosen;
    % Columns 2--4 give statistics describing the window sizes used for most analyses for each dataset
    % (windows had a fixed number of SNPs).
    % The final column gives the percent variance explained by the top two principal components,
    % averaged across independent PCA of each window.
    \label{tab:data_stats}
}
\end{table}

@@

%%%%%%%%%%%
\subsection{Validation}

Address
mutation rate variation;
recombination rate variation;
choice of number of PCs;
choice of window size;
variation in missingness;
maybe differing sample sizes and reweighting.
